Analysing the three-dimensional structure of {\em P. falciparum}

### 2017-07-26 doc/manuscript/paper.tex
Added peng et al

With more than 217 millions cases nearly 429 000 deaths in 2015,  malaria
remains a major disease burden in tropical and subtropical countries and an
impediment to economic development. In Africa, where more than 90\% of the
cases and deaths occurs, the effects of malaria extend far beyond direct
measures of mortality and the disease is thought to cost more than US\$21
billion a year \citep{onwujekwe:do}.
Malaria is caused by small unicellular protozoan {\em Plasmodium}, infecting
its host through a mosquito bite. Out of the 5 species that can infect human,
{\em P. falciparum} is by the far the most deadly with 99\% of the deaths
associated to it. The parasite has a complex life cycle, with multiple stages
both in the human and mosquito host. The human host is infected with
\textit{sporozoites} through the bite of a infected female  {\em Anopheles}
mosquito. The \textit{sporozoites} quickly migrate to the liver, where they
start a two weeks multiplication process. They are then released as
\textit{merozoites} in the bloodstream and proceed to infect red blood cells. The
parasites then start their ``erythrocytic'' cycle (through \textit{rings},
\textit{trophozoites} and \textit{schizonts} stages), via another round of
replications in red blood cells, through an unusual process of cell division
called \textit{schizogony}. The parasite first undergoes multiple rounds of nuclear
replication and division into 13 to 32 daughter cells, until the red blood
cell bursts and provokes the release of \textit{merezoites} and the infective cycle
starts anew. This asexual replication cycle is responsible for the symptoms
and the complications of the disease: anemia, tertian fever, \dots

@@

@@

\begin{table*}
\scriptsize
\centering
\begin{tabular}{rccccccccc}
\hline
\multirow{2}{*}{\textbf{Paper}} & \multirow{2}{*}{\textbf{Organism}} &
\textbf{Full or}
& \textbf{Counts-to-distance} &
\multicolumn{4}{c}{\multirow{2}{*}{\textbf{Constraints}}}
& \multirow{2}{*}{\textbf{Weights}}\\
 & & \textbf{partial} & \textbf{mapping} &  \\
 \cmidrule(lr){5-8} 
 & & & & Adj. & rDNA & C & T & \\
\hline
\cite{dekker:capturing} & {\em S. cerevisiae} & Chr III & Worm-like chain
behavior & & & & \\
\cite{duan:three-dimensional} & {\em S. cerevisiae} & Whole-genome & Linear
relationship & \CHECK &  \CHECK & \CHECK &  & \\
\cite{tanizawa:mapping} & {\em S. pombe} & Whole-genome &
FISH-derived relationship & \CHECK & \CHECK & \CHECK & \CHECK &  \\
\cite{ay:three-dimensional} & {\em P. falciparum} & Whole-genome & Fractal
globule derived relationship & \CHECK  & & &
 & $\frac{1}{\delta_{ij}^2}$ \\
\cite{lesne:3d} & & Whole-genome & \textit{ad hoc} & & & & & \
\end{tabular}
\caption{Differences between MDS-based methods}{}
\label{table:mds_detail}
\end{table*}

@@

\begin{table}[ht!]
\begin{center}
\scriptsize
\begin{tabular}{rlccccc}
\hline
\multirow{2}{*}{\textbf{\footnotesize Publication}} & \multirow{2}{*}{\textbf{\footnotesize Name}} &
\textbf{\footnotesize Consensus or} 
&\multirow{2}{*}{\textbf{\footnotesize MDS-based}} & \textbf{\footnotesize Statistical} &
\multirow{2}{*}{\textbf{\footnotesize Available}} \\
& & \textbf{\footnotesize Ensemble}
 & & \textbf{\footnotesize model} & \\
\hline
\hline
\scriptsize{\cite{dekker:capturing}} & & C & \CHECK & & \\
\scriptsize{\cite{duan:three-dimensional}} &  & C & \CHECK & & \CHECK \\
\scriptsize{\cite{tanizawa:mapping}} & & C & \CHECK & & \\
\scriptsize{\cite{ay:three-dimensional}} & & C & \CHECK & & \\
\scriptsize{\cite{ben-elazar:spatial}} & & C & \CHECK & & \CHECK \\
\scriptsize{\cite{varoquaux:statistical}} & Pastis & C & & \CHECK & \CHECK\\
\scriptsize{\cite{bau:three-dimensional}} & & E & & &  \\
\scriptsize{\cite{umbarger:three-dimensional}} & & E  & & &\\
\scriptsize{\cite{zhang:inference}} & chromSDE & C &  \CHECK & & \CHECK\\
\scriptsize{\cite{rousseau:three}} & & E & & \CHECK & \CHECK\\
\scriptsize{\cite{hu:bayesian}} & Bach & E/C &  & \CHECK & \CHECK\\
\scriptsize{\cite{kalhor:genome}} & & E &   & &\\
\scriptsize{\cite{lesne:3d}} & ShRec3D & C  & \CHECK & & \CHECK \\
\scriptsize{\cite{trieu:large}} & & C & & & \\
\scriptsize{\cite{trieu:3D}} & & C & &  & \\
\scriptsize{\cite{trieu:MOGEN}} & MOGEN & C & & & \\
\scriptsize{\cite{nagano:single-cell}} & & E & & & \\
\scriptsize{\cite{paulsen:manifold}} & & C & \CHECK & & \CHECK \\
\hline
\end{tabular}
\end{center}
\caption{\bf A comparison of 3D inference methods}{In this table, we summarize
properties of published methods to infer the 3D structure of the genome: (1)
is it a consensus or a ensemble based inference? (2) Is it an MDS based
method? (3) or relies on a statistical modeling; (4) is the software
available or not (to the best of our knowledge).}
\end{table}

>>>>

With more than 217 millions cases nearly 429 000 deaths in 2015,  malaria
remains a major disease burden in tropical and subtropical countries and an
impediment to economic development. In Africa, where more than 90\% of the
cases and deaths occurs, the effects of malaria extend far beyond direct
measures of mortality and the disease is thought to cost more than US\$21
billion a year \citep{onwujekwe:do}.
Malaria is caused by small unicellular protozoan {\em Plasmodium}, infecting
its host through a mosquito bite. Out of the 5 species that can infect human,
{\em P. falciparum} is by the far the most deadly with 99\% of the deaths
associated to it. The parasite has a complex life cycle, with multiple stages
both in the human and mosquito host. \sout{The human host is infected with
\textit{sporozoites} through the bite of a infected female  {\em Anopheles}
mosquito. The \textit{sporozoites} quickly migrate to the liver, where they
start a two weeks multiplication process. They are then released as
\textit{merozoites} in the bloodstream and proceed to infect red blood cells. The
parasites then start their ``erythrocytic'' cycle (through \textit{rings},
\textit{trophozoites} and \textit{schizonts} stages), via another round of
replications in red blood cells, through an unusual process of cell division
called \textit{schizogony}. The parasite first undergoes multiple rounds of nuclear
replication and division into 13 to 32 daughter cells, until the red blood
cell bursts and provokes the release of \textit{merezoites} and the infective cycle
starts anew. This asexual replication cycle is responsible for the symptoms
and the complications of the disease: anemia, tertian fever, \dots}

@@

The objective function $\mathcal{O}$, sometimes called the ``scoring
function''

@@

\begin{table*}
\scriptsize
\centering
\begin{tabular}{rccccccccc}
\hline
\multirow{2}{*}{\textbf{Paper}} & \multirow{2}{*}{\textbf{Organism}} &
\textbf{Full or}
& \textbf{Counts-to-distance} &
\multicolumn{4}{c}{\multirow{2}{*}{\textbf{Constraints}}}
& \multirow{2}{*}{\textbf{Weights}}\\
 & & \textbf{partial} & \textbf{mapping} &  \\
 \cmidrule(lr){5-8} 
 & & & & Adj. & rDNA & C & T & \\
\hline
\cite{dekker:capturing} & {\em S. cerevisiae} & Chr III & Worm-like chain
behavior & & & & \\
\cite{duan:three-dimensional} & {\em S. cerevisiae} & Whole-genome & Linear
relationship & \CHECK &  \CHECK & \CHECK &  & \\
\cite{tanizawa:mapping} & {\em S. pombe} & Whole-genome &
FISH-derived relationship & \CHECK & \CHECK & \CHECK & \CHECK &  \\
\cite{ay:three-dimensional} & {\em P. falciparum} & Whole-genome & Fractal
globule derived relationship & \CHECK  & & &
& $\frac{1}{\delta_{ij}^2}$ \\
\cite{peng:sequencing} & {\em P. falciparum} & Whole-genome & Fractal
globule derived relationship & \CHECK  & & &
 & $\frac{1}{\delta_{ij}^2}$ \\
\cite{lesne:3d} & & Whole-genome & \textit{ad hoc} & & & & & \
\end{tabular}
\caption{Differences between MDS-based methods}{}
\label{table:mds_detail}
\end{table*}

@@

\begin{table}[ht!]
\begin{center}
\scriptsize
\begin{tabular}{rlccccc}
\hline
\multirow{2}{*}{\textbf{\footnotesize Publication}} & \multirow{2}{*}{\textbf{\footnotesize Name}} &
\textbf{\footnotesize Consensus or} 
&\multirow{2}{*}{\textbf{\footnotesize MDS-based}} & \textbf{\footnotesize Statistical} &
\multirow{2}{*}{\textbf{\footnotesize Available}} \\
& & \textbf{\footnotesize Ensemble}
 & & \textbf{\footnotesize model} & \\
\hline
\hline
\scriptsize{\cite{dekker:capturing}} & & C & \CHECK & & \\
\scriptsize{\cite{duan:three-dimensional}} &  & C & \CHECK & & \CHECK \\
\scriptsize{\cite{tanizawa:mapping}} & & C & \CHECK & & \\
\scriptsize{\cite{ay:three-dimensional}} & & C & \CHECK & & \\
\scriptsize{\cite{ben-elazar:spatial}} & & C & \CHECK & & \CHECK \\
\scriptsize{\cite{varoquaux:statistical}} & Pastis & C & & \CHECK & \CHECK\\
\scriptsize{\cite{bau:three-dimensional}} & & E & & &  \\
\scriptsize{\cite{umbarger:three-dimensional}} & & E  & & &\\
\scriptsize{\cite{zhang:inference}} & chromSDE & C &  \CHECK & & \CHECK\\
\scriptsize{\cite{peng:sequencing}} & autochrom3D & C &  \CHECK & & \CHECK\\
\scriptsize{\cite{rousseau:three}} & & E & & \CHECK & \CHECK\\
\scriptsize{\cite{hu:bayesian}} & Bach & E/C &  & \CHECK & \CHECK\\
\scriptsize{\cite{kalhor:genome}} & & E &   & &\\
\scriptsize{\cite{lesne:3d}} & ShRec3D & C  & \CHECK & & \CHECK \\
\scriptsize{\cite{trieu:large}} & & C & & & \\
\scriptsize{\cite{trieu:3D}} & & C & &  & \\
\scriptsize{\cite{trieu:MOGEN}} & MOGEN & C & & & \\
\scriptsize{\cite{nagano:single-cell}} & & E & & & \\
\scriptsize{\cite{paulsen:manifold}} & & C & \CHECK & & \CHECK \\
\hline
\end{tabular}
\end{center}
\caption{\bf A comparison of 3D inference methods}{In this table, we summarize
properties of published methods to infer the 3D structure of the genome: (1)
is it a consensus or a ensemble based inference? (2) Is it an MDS based
method? (3) or relies on a statistical modeling; (4) is the software
available or not (to the best of our knowledge).}
\end{table}
